Model LF

### 2022-12-16 paper version 2.Rmd
Commit

COMMENT> 
BEHAVIORAL> prod_ds_shock
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_shock) =  pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_4* TSDELTALOG(TSLAG(wage_ds,1)) +
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_ds_shock,1))+
pr_11* LOG(TSLAG(wage_ds,2))
COEFF>  pr_1 pr_2 pr_3 pr_4 pr_8 pr_9 pr_10 pr_11
STORE> coe(222)

COMMENT> mulighed for at ændrer i produktions funktionen
BEHAVIORAL> prod_ds_sens
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_sens) =  pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_4* TSDELTALOG(TSLAG(wage_ds,1)) +
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_ds_sens,1))+
pr_11* LOG(TSLAG(wage_ds,2))
COEFF>  pr_1 pr_2 pr_3 pr_4 pr_8 pr_9 pr_10 pr_11
STORE> coe(223)

COMMENT> 
IDENTITY> prod
EQ> prod=prodk * (y/yk)
if> shock_prod_model <= 0
IDENTITY> prod
EQ> prod =  prod_ds +alpha_150 + alpha_151*SD1 + alpha_152*SD2 + alpha_153*SD3 - mean_prod
IF> shock_prod_model > 0

COMMENT> 
IDENTITY> i_bd_nfc_k_ds
EQ> i_bd_nfc_k_ds= i_bd_nfc_k_ds_used
if> disc <= 0
IDENTITY> i_bd_nfc_k_ds
EQ> i_bd_nfc_k_ds= i_bd_nfc_k_ds_disc
if> disc > 0

COMMENT> 
IDENTITY> prodk
EQ> prodk=prod * (yk/y)
IF> shock_prod_model > 0

COMMENT> 
IDENTITY> prod_ds
EQ> prod_ds = prodk_ds * (y_ds/yk_ds)
IF> shock_prod_model <= 0
IDENTITY> prod_ds
EQ> prod_ds= prod_ds_shock
if> shock_prod_model > 0 & sens_3 <= 0
IDENTITY> prod_ds
EQ> prod_ds= prod_ds_sens
if> shock_prod_model > 0 & sens_3 > 0

IDENTITY> prodk_ds
EQ> prodk_ds=prod_ds * (yk_ds/y_ds)
IF> shock_prod_model > 0

@@

```{r}
shock_lf_model_shock=shock_lf_model %>% window(start= c(2006,3))
```

@@

 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds

@@

```{r}
plot(part_bs1, col= "green", main= "Participation rate", ylab= "Participation rate (Ratio)"); lines(part, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

```{r}
shock_wage_ds_model_shock=shock_wage_ds_model %>% window(start= c(2006,3))
```

@@

 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
shock_prod_model_shock=shock_prod_model %>% window(start= c(2006,3))
```

@@

 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
plot(prod_bs3, col= "green"); lines(prod, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

## Baseline Scenario 4

```{r}
shock_kuld_model_shock=shock_kuld_model %>% window(start= c(2006,3))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs4 <- list(

```{r}
# Simulate the model (following shock)
Shock_bs4 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs4
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs4 = Shock_bs4$simulation$max_dp
wage_bs4 = Shock_bs4$simulation$wage
komp_r_bs4 = Shock_bs4$simulation$komp_r
part_bs4 = Shock_bs4$simulation$part
yk_ds_bs4 = Shock_bs4$simulation$yk_ds
pc_ds_bs4 = Shock_bs4$simulation$pc_ds
wage_ds_t_bs4 = Shock_bs4$simulation$wage_ds_t
ur_ds_bs4 = Shock_bs4$simulation$ur_ds
emp_bs4 = Shock_bs4$simulation$emp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds

tilpas_pr_bs4 = Shock_bs4$simulation$tilpas_pr
u_ds_bs4 = Shock_bs4$simulation$u_ds
part_bs4 = Shock_bs4$simulation$part
nben_h_bs4 = Shock_bs4$simulation$nben_h
wage_ds_bs4 = Shock_bs4$simulation$wage_ds
dp_person_bs4 = Shock_bs4$simulation$dp_person
kont_h_ratio_bs4 = Shock_bs4$simulation$kont_h_ratio

nl_g_bs4 = Shock_bs4$simulation$nl_g
unemp_bs4 = Shock_bs4$simulation$unemp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
wage_gap1_bs4 = Shock_bs4$simulation$wage_gap1
wage_gap_bs4 = Shock_bs4$simulation$wage_gap
prod_bs4 = Shock_bs4$simulation$prod
```

## Baseline Scenario 5

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs56 <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs56 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs56
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs56 = Shock_bs56$simulation$max_dp
wage_bs56 = Shock_bs56$simulation$wage
komp_r_bs56 = Shock_bs56$simulation$komp_r
part_bs56 = Shock_bs56$simulation$part
yk_ds_bs56 = Shock_bs56$simulation$yk_ds
pc_ds_bs56 = Shock_bs56$simulation$pc_ds
wage_ds_t_bs56 = Shock_bs56$simulation$wage_ds_t
ur_ds_bs56 = Shock_bs56$simulation$ur_ds
emp_bs56 = Shock_bs56$simulation$emp
yd_hk_ds_bs56 = Shock_bs56$simulation$yd_hk_ds

tilpas_pr_bs56 = Shock_bs56$simulation$tilpas_pr
u_ds_bs56 = Shock_bs56$simulation$u_ds
part_bs56 = Shock_bs56$simulation$part
nben_h_bs56 = Shock_bs56$simulation$nben_h
wage_ds_bs56 = Shock_bs56$simulation$wage_ds
dp_person_bs56 = Shock_bs56$simulation$dp_person
kont_h_ratio_bs56 = Shock_bs56$simulation$kont_h_ratio

nl_g_bs56 = Shock_bs56$simulation$nl_g
unemp_bs56 = Shock_bs56$simulation$unemp
yd_hk_ds_bs56 = Shock_bs56$simulation$yd_hk_ds
wage_gap1_bs56 = Shock_bs56$simulation$wage_gap1
wage_gap_bs56 = Shock_bs56$simulation$wage_gap
prod_bs56 = Shock_bs56$simulation$prod
```

## Baseline Scenario 5b Sens all

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs5b <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 sens_3 = TIMESERIES(sens_3+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs5b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs5b
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs5b = Shock_bs5b$simulation$max_dp
wage_bs5b = Shock_bs5b$simulation$wage
komp_r_bs5b = Shock_bs5b$simulation$komp_r
part_bs5b = Shock_bs5b$simulation$part
yk_ds_bs5b = Shock_bs5b$simulation$yk_ds
pc_ds_bs5b = Shock_bs5b$simulation$pc_ds
wage_ds_t_bs5b = Shock_bs5b$simulation$wage_ds_t
ur_ds_bs5b = Shock_bs5b$simulation$ur_ds
emp_bs5b = Shock_bs5b$simulation$emp
yd_hk_ds_bs5b = Shock_bs5b$simulation$yd_hk_ds

tilpas_pr_bs5b = Shock_bs5b$simulation$tilpas_pr
u_ds_bs5b = Shock_bs5b$simulation$u_ds
part_bs5b = Shock_bs5b$simulation$part
nben_h_bs5b = Shock_bs5b$simulation$nben_h
wage_ds_bs5b = Shock_bs5b$simulation$wage_ds
dp_person_bs5b = Shock_bs5b$simulation$dp_person
kont_h_ratio_bs5b = Shock_bs5b$simulation$kont_h_ratio

nl_g_bs5b = Shock_bs5b$simulation$nl_g
unemp_bs5b = Shock_bs5b$simulation$unemp
yd_hk_ds_bs5b = Shock_bs5b$simulation$yd_hk_ds
wage_gap1_bs5b = Shock_bs5b$simulation$wage_gap1
wage_gap_bs5b = Shock_bs5b$simulation$wage_gap
prod_bs5b = Shock_bs5b$simulation$prod
```

## Baseline Scenario 7 all but prod and wage

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs7 <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs7 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs7
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs7 = Shock_bs7$simulation$max_dp
wage_bs7 = Shock_bs7$simulation$wage
komp_r_bs7 = Shock_bs7$simulation$komp_r
part_bs7 = Shock_bs7$simulation$part
yk_ds_bs7 = Shock_bs7$simulation$yk_ds
pc_ds_bs7 = Shock_bs7$simulation$pc_ds
wage_ds_t_bs7 = Shock_bs7$simulation$wage_ds_t
ur_ds_bs7 = Shock_bs7$simulation$ur_ds
emp_bs7 = Shock_bs7$simulation$emp
yd_hk_ds_bs7 = Shock_bs7$simulation$yd_hk_ds

tilpas_pr_bs7 = Shock_bs7$simulation$tilpas_pr
u_ds_bs7 = Shock_bs7$simulation$u_ds
part_bs7 = Shock_bs7$simulation$part
nben_h_bs7 = Shock_bs7$simulation$nben_h
wage_ds_bs7 = Shock_bs7$simulation$wage_ds
dp_person_bs7 = Shock_bs7$simulation$dp_person
kont_h_ratio_bs7 = Shock_bs7$simulation$kont_h_ratio

nl_g_bs7 = Shock_bs7$simulation$nl_g
unemp_bs7 = Shock_bs7$simulation$unemp
yd_hk_ds_bs7 = Shock_bs7$simulation$yd_hk_ds
wage_gap1_bs7 = Shock_bs7$simulation$wage_gap1
wage_gap_bs7 = Shock_bs7$simulation$wage_gap
prodk_bs7 = Shock_bs7$simulation$prodk
```

## Baseline Scenario 7b

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs7b <- list(

```{r}
# Simulate the model (following shock)
Shock_bs7b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs7b
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs7b = Shock_bs7b$simulation$max_dp
wage_bs7b = Shock_bs7b$simulation$wage
komp_r_bs7b = Shock_bs7b$simulation$komp_r
part_bs7b = Shock_bs7b$simulation$part
yk_ds_bs7b = Shock_bs7b$simulation$yk_ds
pc_ds_bs7b = Shock_bs7b$simulation$pc_ds
wage_ds_t_bs7b = Shock_bs7b$simulation$wage_ds_t
ur_ds_bs7b = Shock_bs7b$simulation$ur_ds
emp_bs7b = Shock_bs7b$simulation$emp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
prodk_bs7b = Shock_bs7b$simulation$prodk
tilpas_pr_bs7b = Shock_bs7b$simulation$tilpas_pr
u_ds_bs7b = Shock_bs7b$simulation$u_ds
part_bs7b = Shock_bs7b$simulation$part
nben_h_bs7b = Shock_bs7b$simulation$nben_h
wage_ds_bs7b = Shock_bs7b$simulation$wage_ds
dp_person_bs7b = Shock_bs7b$simulation$dp_person
kont_h_ratio_bs7b = Shock_bs7b$simulation$kont_h_ratio
lf_bs7b = Shock_bs7b$simulation$lf
nl_g_bs7b = Shock_bs7b$simulation$nl_g
unemp_bs7b = Shock_bs7b$simulation$unemp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
wage_gap1_bs7b = Shock_bs7b$simulation$wage_gap1
wage_gap_bs7b = Shock_bs7b$simulation$wage_gap
prod_bs7b = Shock_bs7b$simulation$prod
ur_test_bs7b = Shock_bs7b$simulation$ur_test
ur_bs7b = Shock_bs7b$simulation$ur

y_bs7b = Shock_bs7b$simulation$y
yk_bs7b = Shock_bs7b$simulation$yk

y_yk_bs7= yk_bs7b/y_bs7b
```

## Baseline Scenario 8

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs8 <- list(

```{r}
# Simulate the model (following shock)
Shock_bs8 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs8
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs8 = Shock_bs8$simulation$max_dp
wage_bs8 = Shock_bs8$simulation$wage
komp_r_bs8 = Shock_bs8$simulation$komp_r
part_bs8 = Shock_bs8$simulation$part
yk_ds_bs8 = Shock_bs8$simulation$yk_ds
pc_ds_bs8 = Shock_bs8$simulation$pc_ds
wage_ds_t_bs8 = Shock_bs8$simulation$wage_ds_t
ur_ds_bs8 = Shock_bs8$simulation$ur_ds
emp_bs8 = Shock_bs8$simulation$emp
yd_hk_ds_bs8 = Shock_bs8$simulation$yd_hk_ds
prodk_bs8 = Shock_bs8$simulation$prodk
tilpas_pr_bs8 = Shock_bs8$simulation$tilpas_pr
u_ds_bs8 = Shock_bs8$simulation$u_ds
part_bs8 = Shock_bs8$simulation$part
nben_h_bs8 = Shock_bs8$simulation$nben_h
wage_ds_bs8 = Shock_bs8$simulation$wage_ds
dp_person_bs8 = Shock_bs8$simulation$dp_person
kont_h_ratio_bs8 = Shock_bs8$simulation$kont_h_ratio
lf_bs8 = Shock_bs8$simulation$lf
nl_g_bs8 = Shock_bs8$simulation$nl_g
unemp_bs8 = Shock_bs8$simulation$unemp
yd_hk_ds_bs8 = Shock_bs8$simulation$yd_hk_ds
wage_gap1_bs8 = Shock_bs8$simulation$wage_gap1
wage_gap_bs8 = Shock_bs8$simulation$wage_gap
prod_bs8 = Shock_bs8$simulation$prod
ur_test_bs8 = Shock_bs8$simulation$ur_test
ur_bs8 = Shock_bs8$simulation$ur
y_bs8 = Shock_bs8$simulation$y
yk_bs8 = Shock_bs8$simulation$yk
```

## Baseline Scenario 9 pp

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs9 <- list(

  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs9 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs9
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs9 = Shock_bs9$simulation$max_dp
wage_bs9 = Shock_bs9$simulation$wage
komp_r_bs9 = Shock_bs9$simulation$komp_r
part_bs9 = Shock_bs9$simulation$part
yk_ds_bs9 = Shock_bs9$simulation$yk_ds
pc_ds_bs9 = Shock_bs9$simulation$pc_ds
wage_ds_t_bs9 = Shock_bs9$simulation$wage_ds_t
ur_ds_bs9 = Shock_bs9$simulation$ur_ds
emp_bs9 = Shock_bs9$simulation$emp
yd_hk_ds_bs9 = Shock_bs9$simulation$yd_hk_ds
prodk_bs9 = Shock_bs9$simulation$prodk
tilpas_pr_bs9 = Shock_bs9$simulation$tilpas_pr
u_ds_bs9 = Shock_bs9$simulation$u_ds
part_bs9 = Shock_bs9$simulation$part
nben_h_bs9 = Shock_bs9$simulation$nben_h
wage_ds_bs9 = Shock_bs9$simulation$wage_ds
dp_person_bs9 = Shock_bs9$simulation$dp_person
kont_h_ratio_bs9 = Shock_bs9$simulation$kont_h_ratio
lf_bs9 = Shock_bs9$simulation$lf
nl_g_bs9 = Shock_bs9$simulation$nl_g
unemp_bs9 = Shock_bs9$simulation$unemp
yd_hk_ds_bs9 = Shock_bs9$simulation$yd_hk_ds
wage_gap1_bs9 = Shock_bs9$simulation$wage_gap1
wage_gap_bs9 = Shock_bs9$simulation$wage_gap
prod_bs9 = Shock_bs9$simulation$prod
ur_test_bs9 = Shock_bs9$simulation$ur_test
ur_bs9 = Shock_bs9$simulation$ur
y_bs9 = Shock_bs9$simulation$y
yk_bs9 = Shock_bs9$simulation$yk
```

## Scenario 0 lf

```{r}
# Define add-factor list (defining shock)
constantAdjList0 <- list(

 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
  shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_0 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList0
                    )
```

```{r}
###Gengivelse af stød til model
part_000 = Shock_0$simulation$part
unemp_000 = Shock_0$simulation$unemp
komp_r_000 = Shock_0$simulation$komp_r
part_000 = Shock_0$simulation$part
yk_ds_000 = Shock_0$simulation$yk_ds
pc_ds_000 = Shock_0$simulation$pc_ds
wage_ds_t_000 = Shock_0$simulation$wage_ds_t
ur_ds_000 = Shock_0$simulation$ur_ds
emp_000 = Shock_0$simulation$emp
yd_hk_ds_000 = Shock_0$simulation$yd_hk_ds
lf_000 = Shock_0$simulation$lf
tilpas_pr_000 = Shock_0$simulation$tilpas_pr
u_ds_000 = Shock_0$simulation$u_ds
part_000 = Shock_0$simulation$part
nben_h_000 = Shock_0$simulation$nben_h
wage_ds_000 = Shock_0$simulation$wage_ds
dp_person_000 = Shock_0$simulation$dp_person
kont_h_ratio_000 = Shock_0$simulation$kont_h_ratio

nl_g_000 = Shock_0$simulation$nl_g
prodk_ds_000 = Shock_0$simulation$prodk_ds
yd_hk_ds_000 = Shock_0$simulation$yd_hk_ds
wage_gap1_000 = Shock_0$simulation$wage_gap1
wage_gap_000 = Shock_0$simulation$wage_gap
prod_000 = Shock_0$simulation$prod
```

```{r}
plot(part_000, col= "red"); lines(part_bs1, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()
```

```{r}
plot(prod_000, col= "red"); lines(prod_bs1, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()

prod_000 - prod_bs1

plot(((yk_ds_000 - yk_ds_bs1) / yk_ds_bs1), col= "black", xlab= "Year", ylab= "% Change in gdp");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((unemp_000 - unemp_bs1) / unemp_bs1), col= "black", xlab= "Year", ylab= "% Change in employment");
legend("top", legend=c("Employment"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

```{r}
plot((unemp_000-unemp_bs1)*1000, col= "red");
```

## Scenario 1 reg

@@

 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q')

@@

```{r}
plot(((max_dp_01 - max_dp_00) / max_dp_00), col= "black", xlab= "Year", ylab= "% Change in maximum level of income insurance", main= "Maximum level of incom insurance");
grid()
```

```{r}
plot(part_01, col= "red"); lines(part_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

plot(((dp_person_01 - dp_person_00) / dp_person_00)*100, col= "black", xlab= "Year", main= "Income insurance", ylab= "% Change in avg income insurance");
grid()

plot(((komp_r_01 - komp_r_00) / komp_r_00)*100, col= "black", xlab= "Year", main= "Compensation rate", ylab= "% Change in compensation rate");
grid()
```

@@

plot(((nl_g_01 - nl_g_00)), col= "black", xlab= "Year", main= "Government net lending",  ylab= "Change in government net lending");
grid()

plot(((yd_hk_ds_01 - yd_hk_ds_00) / yd_hk_ds_00)*100, col= "black", xlab= "Year", main= "Households disp. income", ylab= "% Change in households disposable income");
grid()
```

@@

plot(((yk_ds_01 - yk_ds_00) / yk_ds_00)*100, col= "black", xlab= "Year", main="GDP", ylab= "% Change in gdp");
grid()

plot(((emp_01 - emp_00) / emp_00)*100, col= "black", xlab= "Year", main= "Employment", ylab= "% Change in employment");
grid()
```

@@

```{r}
plot((unemp_01-unemp_00)*1000, col= "red")
```

```{r}
plot((nl_g_01-nl_g_00), col= "red")
```

## Scenario 1b max

```{r}
shock_max_dp_model_shock=shock_max_dp_model %>% window(start= c(2006,3))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList1b <- list(

shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_1b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList1b
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_01b = Shock_1b$simulation$max_dp
wage_01b = Shock_1b$simulation$wage
komp_r_01b = Shock_1b$simulation$komp_r
part_01b = Shock_1b$simulation$part
yk_ds_01b = Shock_1b$simulation$yk_ds
pc_ds_01b = Shock_1b$simulation$pc_ds
wage_ds_t_01b = Shock_1b$simulation$wage_ds_t
ur_ds_01b = Shock_1b$simulation$ur_ds
emp_01b = Shock_1b$simulation$emp
yd_hk_ds_01b = Shock_1b$simulation$yd_hk_ds

tilpas_pr_01b = Shock_1b$simulation$tilpas_pr
u_ds_01b = Shock_1b$simulation$u_ds
part_01b = Shock_1b$simulation$part
nben_h_01b = Shock_1b$simulation$nben_h
wage_ds_01b = Shock_1b$simulation$wage_ds
dp_person_01b = Shock_1b$simulation$dp_person
kont_h_ratio_01b = Shock_1b$simulation$kont_h_ratio

nl_g_01b = Shock_1b$simulation$nl_g

yd_hk_ds_01b = Shock_1b$simulation$yd_hk_ds
wage_gap1_01b = Shock_1b$simulation$wage_gap1
wage_gap_01b = Shock_1b$simulation$wage_gap
prod_01b = Shock_1b$simulation$prod
```

```{r}
plot(((max_dp_01b - max_dp_00) / max_dp_00), col= "black", xlab= "Year", ylab= "% Change in maximum level of income insurance", main= "Maximum level of incom insurance");
grid()
```

## Scenario 2 reg wage

@@

```{r}
plot(wage_ds_02, col= "red"); lines(wage_ds_bs2, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

>>>>

COMMENT> 
IDENTITY> prod
EQ> prod=prodk * (y/yk)

COMMENT> 
IDENTITY> prod_ds
EQ> prod_ds = prodk_ds * (y_ds/yk_ds)

@@

```{r}
shock_wage_ds_model_shock=shock_wage_ds_model %>% window(start= c(2006,3))
shock_kuld_model_shock=shock_kuld_model %>% window(start= c(2006,3))
shock_lf_model_shock=shock_lf_model %>% window(start= c(2006,3))
```

@@

shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds
max_dp_bs1 = Shock_bs1$simulation$max_dp

@@

@@

@@

@@

@@

@@

## Scenario 1

@@

shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
plot(((max_dp_01 - max_dp_bs1) / max_dp_bs1), col= "black", xlab= "Year", ylab= "% Change in maximum level of income insurance", main= "Maximum level of incom insurance");
grid()
```

```{r}
plot(part_01, col= "red"); lines(part_bs1, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

plot(((dp_person_01 - dp_person_bs1) / dp_person_bs1)*100, col= "black", xlab= "Year", main= "Income insurance", ylab= "% Change in avg income insurance");
grid()

plot(((komp_r_01 - komp_r_bs1) / komp_r_bs1)*100, col= "black", xlab= "Year", main= "Compensation rate", ylab= "% Change in compensation rate");
grid()
```

@@

plot(((nl_g_01 - nl_g_bs1)), col= "black", xlab= "Year", main= "Government net lending",  ylab= "Change in government net lending");
grid()

plot(((yd_hk_ds_01 - yd_hk_ds_bs1) / yd_hk_ds_bs1)*100, col= "black", xlab= "Year", main= "Households disp. income", ylab= "% Change in households disposable income");
grid()
```

@@

plot(((yk_ds_01 - yk_ds_bs1) / yk_ds_bs1)*100, col= "black", xlab= "Year", main="GDP", ylab= "% Change in gdp");
grid()

plot(((emp_01 - emp_bs1) / emp_bs1)*100, col= "black", xlab= "Year", main= "Employment", ylab= "% Change in employment");
grid()
```

@@

```{r}
plot((unemp_01-unemp_bs1)*1000, col= "red")
```

```{r}
plot((nl_g_01-nl_g_bs1), col= "red")
```

## Scenario 2

@@

## Scenario 3
